Volunteers in the Clouds: an Architecture for Low Cost and Potentially Massive Distributed Evolutionary Computation

### 2015-10-27 special-issue-ci/volunteer-clouds-ieee-ci-si.tex
Minor suggestions

This kind of systems must solve a series of issues before even starting to 
measure their performance; these issues are related to security as well as
safety, which introduces a {\em social} aspect to the design of a
computing system that makes it a {\em techno-social system}
\cite{vespignani2009predicting}. In this paper our intention is to
present the {\sf NodIO} framework and analyze it from two different
angles: the purely technical angle, including the decisions that went
into its features, and the social angle, to account on how the persons
that voluntarily choose to enter the web page that runs the system
determine its performance and how it can be modeled and, eventually,
predicted.

>>>>

%PABLO: He añadido el siguiente párrafo para el issue #31
There exist other volunteer frameworks written in compiled languages, such as C++ or Java, that can achieve more performance than JavaScript. However, one of the advantages of our system is that clients do not need to install anything in their machines, they just need to open a regular web page  
% Somewhat redundant 
% Javascript is the only language that can be executed in this way without any installation, 
% also removed the default, redundant with next sentence
in modern browsers, such as Chrome, Safari or Firefox, that are available in almost every desktop or mobile device. Other advantage is that the source code can be directly examined by the volunteer, not being compiled as other options (such as Java Applets or ActiveX). Also, as we discuss in this paper, it can provide some extra features such as enhanced security or operating system independence.

%PABLO: hay que enlazar con el siguiente párrafo
This kind of systems must solve a series of issues before even starting to 
measure their performance; these issues are related to security as well as
safety, which introduces a {\em social} aspect to the design of a
computing system that makes it a {\em techno-social system}
\cite{vespignani2009predicting}. In this paper our intention is to
present the {\sf NodIO} framework and analyze it from two different
angles: the purely technical angle, including the decisions that went
into its features, and the social angle, to account on how the persons
that voluntarily choose to enter the web page that runs the system
determine its performance and how it can be modeled and, eventually,
predicted.
